Influence of galaxy rotation and outflows in the Lyman Alpha spectral line

### 2017-03-02 paper/paper.tex
now i need to update plots

\subsection{Doppler shift in frequency}

Rotations induces a Doppler shift of the only-outflow spectra.\\

@@

TERMINAR...\\
PONER GRAFICA REAL...\\

@@

The conclusions obtained from this work are: \\

\begin{itemize}
	\item The outgoing spectra depend on the angle an external observer is viewing the galaxy from. The closer it is to the equator of the galaxy, the higher the central valley of the frequency distribution. \\

	\item The effects of \vrot, \vout and \tauh are consistent with the different authors that have used them. \vrot broadens the \lya line. \vout increases the peaks asymmetry and \tauh induces a redshift around the zero velocity.\\

	\item Rotations induces a Doppler shift in frequency of the only-outflow spectra.\\

>>>>

\subsection{Doppler shift by rotation}

The rotation effect induces a Doppler shift in frequency and displaces the only-outflow spectra. As seen in Fig. \ref{fig:rotation_doppler_outflow} rotation takes the resulting spectrum with \vrot$=0$ and displaces it from its central location. Then it weights the lines and they all merge into the resulting red \lya line.\\

@@

PONER GRAFICA REAL...\\

@@

The conclusions obtained from this work are:

\begin{itemize}
	\item The outgoing spectra depend on the angle an external observer is viewing the galaxy from. The closer it is to the equator of the galaxy, the higher the central valley of the frequency distribution.

	\item The effects of \vrot, \vout and \tauh are consistent with the different authors that have used them. \vrot broadens the \lya line. \vout increases the peaks asymmetry and \tauh induces a redshift around the zero velocity.

	\item Rotations induces a Doppler shift in frequency of the only-outflow spectra.
